---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

 [![Travis build status](https://travis-ci.org/mdsumner/ozmaps.svg?branch=master)](https://travis-ci.org/mdsumner/ozmaps)
  [![AppVeyor Build Status](https://ci.appveyor.com/mdsumner/ozmaps)](https://ci.appveyor.com/api/projects/status/github//mdsumner/ozmaps/?branch=master&svg=true)
   [![Coverage status](https://codecov.io/gh/mdsumner/ozmaps/branch/master/graph/badge.svg)](https://codecov.io/github/mdsumner/ozmaps?branch=master)
[![CRAN status](http://www.r-pkg.org/badges/version/ozmaps)](https://cran.r-project.org/package=ozmaps)

 
```{r setup, include = FALSE}
library(dplyr)
library(sf)
library(rmapshaper)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
#knitr::read_chunk("data-raw/download_2016.R")

```
# Overview

The goal of ozmaps is to get maps of Australia to plot!

# Installation

ozmaps may be installed directly from github. 

```{r, eval = FALSE}
devtools::install_github("mdsumner/ozmaps")
```

The package includes some *simple features* data, which can be used
independently of ozmaps with the 'sf' package. If required, install `sf` from CRAN. 

```{r,eval=FALSE}
install.packages("sf")
```

## Usage

Plot Australia with states. 

```{r}
library(ozmaps)
ozmap()

```

Plot Australia without states. 

```{r}
ozmap(states = FALSE)
```

Add to an existing plot. 

```{r}
plot(quakes[c("long", "lat")], xlim = c(120, 190))
ozmap(add = TRUE)
```

Obtain the data used in `sf` form. 

```{r}
sf_oz <- ozmap_data("states")

tibble::as_tibble(sf_oz)
```

Plot with a custom palette. 

```{r}
library(sf)
nmjr <- ochRe::ochre_pal()(dim(sf_oz)[1])
plot(st_geometry(sf_oz), col = nmjr)

## soon...plot directly with ggplot2
library(ggplot2)
ggplot(sf_oz, aes(fill = name)) + geom_sf() + coord_sf(crs = "+proj=lcc +lon_0=135 +lat_0=-30 +lat_1=-10 +lat_2=-45 +datum=WGS84") + scale_fill_manual(values = nmjr)
```


Plot the ABS layers (from 2016). 

```{r}

ozmap("abs_sa4", col = ochRe::ochre_pal()(nrow(abs_sa4)))


ozmap("abs_gccsa", col = ochRe::ochre_pal()(nrow(abs_gccsa)))
```

 Please note that the 'ozmaps' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
