---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Build Status](http://badges.herokuapp.com/travis/mdsumner/ozmaps?branch=master&env=BUILD_NAME=trusty_release&label=ubuntu)](https://travis-ci.org/mdsumner/ozmaps)
[![Build Status](http://badges.herokuapp.com/travis/mdsumner/ozmaps?branch=master&env=BUILD_NAME=osx_release&label=osx)](https://travis-ci.org/mdsumner/ozmaps) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdsumner/ozmaps?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/ozmaps) 
 [![CRAN status](http://www.r-pkg.org/badges/version/ozmaps)](https://cran.r-project.org/package=ozmaps)
 ![cranlogs](http://cranlogs.r-pkg.org./badges/ozmaps)
[![Coverage Status](https://img.shields.io/codecov/c/github/mdsumner/ozmaps/master.svg)](https://codecov.io/github/mdsumner/ozmaps?branch=master)

 
```{r setup, include = FALSE}
library(dplyr)
library(sf)
library(rmapshaper)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
#knitr::read_chunk("data-raw/download_2016.R")

```
# Overview

The goal of ozmaps is to get maps of Australia to plot!

# Installation

ozmaps may be installed directly from github. 

```{r, eval = FALSE}
devtools::install_github("mdsumner/ozmaps")
```

The package includes some *simple features* data, which can be used
independently of ozmaps with the 'sf' package. If required, install `sf` from CRAN. 

```{r,eval=FALSE}
install.packages("sf")
```

## Usage

Plot Australia with states. 

```{r}
library(ozmaps)
ozmap()

```

Plot Australia without states. 

```{r}
ozmap(x = "country")
```

Add to an existing plot. 

```{r}
plot(quakes[c("long", "lat")], xlim = c(120, 190))
ozmap(add = TRUE)
```

Obtain the data used in `sf` form. 

```{r}
sf_oz <- ozmap_data("states")

tibble::as_tibble(sf_oz)
```

Plot with a custom palette. 

```{r}
library(sf)
nmjr <- colorRampPalette(paletteer::paletteer_d(package = "ochRe", palette = "namatjira_qual"))(nrow(sf_oz))
plot(st_geometry(sf_oz), col = nmjr)

## soon...plot directly with ggplot2
library(ggplot2)
ggplot(sf_oz, aes(fill = NAME)) + geom_sf() + coord_sf(crs = "+proj=lcc +lon_0=135 +lat_0=-30 +lat_1=-10 +lat_2=-45 +datum=WGS84") + scale_fill_manual(values = nmjr)
```


Plot the ABS layers (from 2016). 

```{r}
opal <- colorRampPalette(paletteer::paletteer_d(package = "ochRe", palette = "namatjira_qual"))
ozmap("abs_ced", col = opal(nrow(abs_ced)))


ozmap("abs_ste", col = opal(nrow(abs_ste)))
```

---

 Please note that the 'ozmaps' project is released with a [Contributor Code of Conduct](https://github.com/mdsumner/ozmaps/blob/master/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
